

```{r}
rm(list = setdiff(ls(), lsf.str())[!(setdiff(ls(), lsf.str()) %in% "params")])
source(here::here("R", "002-folder_paths_and_options.R"))

# It's input is the following R objects:

adni_lan_recoded_quantile <- readRDS(file=path(r_objects_folder, "025_adni_lan_recoded_quantile.rds"))

```

```{r}

quantile_summary_table <- function(df, x, mytitle) {
  df %>%
    group_by({{ x }}) %>%
    count() %>%
    ungroup() %>%
    mutate(p = 100*n/sum(n)) %>%
    rename(g = {{ x }}) %>%
    gt(rowname_col = "g") %>%
      fmt_number(columns = vars(p),
               decimals = 1) %>%
      tab_header(title = mytitle) %>%
      cols_label(n = "N",
                 p = "%")
}



scatterplot_stratified <- function(df, x, y, strat, mytitle) {
    ggplot(data = df, aes(x = {{ x }}, y = {{ y }}, color = {{strat}})) +
      geom_point(position = "jitter", alpha = .5) +
      geom_smooth(se=FALSE, method = "lm", color = "blue") +
      hrbrthemes::theme_ipsum() +
      scale_color_manual("Group", values = c("#e41a1c", "#377eb8", "#4daf4a", "#984ea3")) +
      ggtitle(mytitle) 
      
}



```

# Summary of the language subdomains by change group

This section summarizes the change in test scores after they are categorized.  The categories are "improve", "no change", and "decline". The scatterplots show the test scores at the first (M0) and second (M6) visits.

## Animal naming (raw score)

The category score ranges are:

1. "improve": 4 - 15 
2. "no change": -3 - 3 
3. "decline": -15 - -4

```{r, out.width = '85%', fig.retina=2}

quantile_summary_table(adni_lan_recoded_quantile, 
                       x = animalsc_raw_change_quantile,
                       mytitle = "Change in animal fluency categorized")

scatterplot_stratified(adni_lan_recoded_quantile, 
  x = animalsc_raw0, 
  y = animalsc_raw_change, 
  strat = animalsc_raw_change_quantile,
  mytitle = "Change in Animal (raw score) vs Animal (raw score) M0") + 
  geom_hline(yintercept = 0)

scatterplot_stratified(adni_lan_recoded_quantile, 
  x = animalsc_raw0, 
  y = animalsc_raw6, 
  strat = animalsc_raw_change_quantile,
  mytitle = "Animal (raw score) M6 vs Animal (raw score) M0") +
  geom_abline(slope = 1)




```



## F fluency (raw score)

The category score ranges are

1. "improve": 4 - 15 
2. "no change": -3 - 3 
3. "decline": -15 - -4

```{r, out.width = '85%', fig.retina=2}
quantile_summary_table(adni_lan_recoded_quantile, 
                       x = ffluency_raw_change_quantile,
                       mytitle = "Change in F fluency categorized")


scatterplot_stratified(adni_lan_recoded_quantile, 
  x = ffluency_raw0, 
  y = ffluency_raw_change, 
  strat = ffluency_raw_change_quantile,
  mytitle = "Change in F fluency (raw score) vs F fluency (raw score) M0") + 
  geom_hline(yintercept = 0)

scatterplot_stratified(adni_lan_recoded_quantile, 
  x = ffluency_raw0, 
  y = ffluency_raw6, 
  strat = ffluency_raw_change_quantile,
  mytitle = "F fluency (raw score) M6 vs F fluency (raw score) M0") +
  geom_abline(slope = 1)

```


## Confrontation naming

The category score ranges are

1. "improve": 0.01 - 3 
2. "no change": 0 
3. "decline": -3 - -0.01

```{r, out.width = '85%', fig.retina=2}

quantile_summary_table(adni_lan_recoded_quantile, 
                       x = confront_change_quantile,
                       mytitle = "Change in confrontation naming categorized")


scatterplot_stratified(adni_lan_recoded_quantile, 
  x = confront0, 
  y = confront_change, 
  strat = confront_change_quantile,
  mytitle = "Change in confrontation naming vs Confrontation naming M0") + 
  geom_hline(yintercept = 0)

scatterplot_stratified(adni_lan_recoded_quantile, 
  x = confront0, 
  y = confront6, 
  strat = confront_change_quantile,
  mytitle = "Confrontation naming M6 vs Confrontation naming M0") +
  geom_abline(slope = 1)
```


## Boston Naming Test

The category score ranges are

1. "improve": 3 - 30 
2. "no change": -2 - 2 
3. "decline": -30 - -3

```{r, out.width = '85%', fig.retina=2}

quantile_summary_table(adni_lan_recoded_quantile, 
                       x = bnt_change_quantile,
                       mytitle = "Change in Boston Naming Test categorized")


scatterplot_stratified(adni_lan_recoded_quantile, 
  x = bnt0, 
  y = bnt_change, 
  strat = bnt_change_quantile,
  mytitle = "Change in Boston Naming Test vs Boston Naming Test M0") + 
  geom_hline(yintercept = 0)

scatterplot_stratified(adni_lan_recoded_quantile, 
  x = bnt0, 
  y = bnt6, 
  strat = bnt_change_quantile,
  mytitle = "Boston Naming Test M6 vs Boston Naming Test M0") +
  geom_abline(slope = 1)
```

## Confrontation naming without BNT

The category score ranges are

1. "improve": 0.01 - 3 
2. "no change": 0 
3. "decline": -3 - -0.01

```{r, out.width = '85%', fig.retina=2}

quantile_summary_table(adni_lan_recoded_quantile, 
                       x = confront_wo_bnt_change_quantile,
                       mytitle = "Change in confrontation naming w/o BNT categorized")


scatterplot_stratified(adni_lan_recoded_quantile, 
  x = confront_wo_bnt0, 
  y = confront_wo_bnt_change, 
  strat = confront_wo_bnt_change_quantile,
  mytitle = "Change in confrontation naming w/o BNT vs Confrontation naming w/o BNT M0") + 
  geom_hline(yintercept = 0)

scatterplot_stratified(adni_lan_recoded_quantile, 
  x = confront_wo_bnt0, 
  y = confront_wo_bnt6, 
  strat = confront_wo_bnt_change_quantile,
  mytitle = "Confrontation naming w/o BNT M6 vs Confrontation naming w/o BNT M0") +
  geom_abline(slope = 1)
```

## Other language items

The category score ranges are

1. "improve": 0.01 - 3 
2. "no change": 0 
3. "decline": -3 - -0.01

```{r, out.width = '85%', fig.retina=2}
quantile_summary_table(adni_lan_recoded_quantile, 
                       x = others_change_quantile,
                       mytitle = "Change in other language items categorized")


scatterplot_stratified(adni_lan_recoded_quantile, 
  x = others0, 
  y = others_change, 
  strat = others_change_quantile,
  mytitle = "Change in other language items vs Other language items M0") + 
  geom_hline(yintercept = 0)

scatterplot_stratified(adni_lan_recoded_quantile, 
  x = others0, 
  y = others6, 
  strat = others_change_quantile,
  mytitle = "Other language items M6 vs Other language items M0") +
  geom_abline(slope = 1)

```

