```{r}
rm(list = setdiff(ls(), lsf.str())[!(setdiff(ls(), lsf.str()) %in% "params")])
source(here::here("R", "002-folder_paths_and_options.R"))

# It's input is the following R objects:
adni.recoded <- readRDS(file=path(r_objects_folder, "025_adni_recoded.rds"))
adni.quantiles <- readRDS(file=path(r_objects_folder, "025_adni_quantiles.rds"))
```


# Summary of quantiled retest scores

This sections summarized the retest scores split into four quantiles.

Higher quantile scores reflect a lower score at follow-up than baseline (or a smaller gain from baseline to follow-up). Lower quantile scores reflects a larger score at follow-up than baseline.  Only "Normal" and "MCI" subjects are used in this analysis.

## Correlation between the retest quantiles

```{r}

adni.quantiles %>%
  select(contains("quantile")) %>%
  select(-contains("group")) %>%
  mutate_all(as.numeric) %>%
  corrr::correlate(method = "spearman", diagonal = 1) %>%
  corrr::shave(upper = TRUE) %>%
  corrr::fashion() %>% 
  mutate_at(vars(contains("quantile")), as.numeric) %>%
  kable(caption = "Correlation matrix of quantiled change scores",
        col.names = c("Domain", "ef_quantile", "mem_quantile", "vsp_quantile", "lang_quantile")) %>%
  kable_styling(bootstrap_options = kable.styling.bootstrap.option, 
                full_width = F, position = kable.styling.position.option) %>%
  column_spec(1, width = "8em") %>%
  column_spec(2, width = "8em") %>%
  column_spec(3, width = "8em") %>%
  column_spec(4, width = "8em") %>%
  column_spec(5, width = "8em") %>%
  row_spec(0, align = "c")


```

## Tables of quantile domain by quantiled domain

```{r}

my_quantile_table <- function(df, x, y, xlab, ylab, myheader) {
  options(knitr.kable.NA = 'NA')
  df %>%
  select({{ x }}, {{ y }}) %>%
  group_by({{ x }}, {{ y }}) %>%
  count() %>%
  spread(key = {{ y }}, value = n) %>%
  kable(caption = str_c(xlab, " vs ", ylab),
        col.names = c(xlab, "1 (best)", "2", "3", "4 (worst)")) %>%
  kable_styling(bootstrap_options = kable.styling.bootstrap.option,
                full_width = F, position = kable.styling.position.option) %>%
  add_header_above(myheader) %>%
    column_spec(1, width = "12em") %>%
    column_spec(2, width = "6em") %>%
    column_spec(3, width = "6em") %>%
    column_spec(4, width = "6em") %>%
    column_spec(5, width = "6em") %>%
  row_spec(0, align = "c")
}
```

```{r}
my_quantile_table(adni.quantiles, mem_quantile, ef_quantile, 
                  "Memory", "Executive Function", 
                  c(" " = 1, "Executive Function" = 4))
```

```{r}
my_quantile_table(adni.quantiles, mem_quantile, lang_quantile, 
                  "Memory", "Language", 
                  c(" " = 1, "Language" = 4))
```

<p class="my-pagebreak"></p>

```{r}
my_quantile_table(adni.quantiles, mem_quantile, vsp_quantile, 
                  "Memory", "Visualspatial", 
                  c(" " = 1, "Visualspatial" = 4))
```

```{r}
my_quantile_table(adni.quantiles, ef_quantile, lang_quantile, 
                  "Executive Function", "Lanugage", 
                  c(" " = 1, "Language" = 4))
```

```{r}
my_quantile_table(adni.quantiles, ef_quantile, vsp_quantile, 
                  "Executive Function", "Visualspatial", 
                  c(" " = 1, "Visualspatial" = 4))
```

```{r}
my_quantile_table(adni.quantiles, lang_quantile, vsp_quantile, 
                  "Language", "Visualspatial", 
                  c(" " = 1, "Visualspatial" = 4))
```

<p class="my-pagebreak"></p>

## Summary of subjects in highest retest quantile

The subjects are combined across quantile retest domains, counting how often they were in the highest quantile.

```{r}
adni.quantiles %>%
  count(quantile_group_collapsed) %>%
  mutate(p = 100*n/sum(n)) %>%
  kable(caption = "Summary of subjects in highest quantile",
        col.names = c("Retest impaired domain", "N", "%"),
        digits = c(0, 0, 1)) %>%
  kable_styling(bootstrap_options = kable.styling.bootstrap.option,
                full_width = F, position = kable.styling.position.option) %>%
  column_spec(2, width = "6em") %>%
  column_spec(3, width = "6em") %>%
  row_spec(0, align = "c")



adni.quantiles %>%
  count(bl_dx, quantile_group_collapsed) %>%
  spread(key = bl_dx, value = n) %>%
  mutate(p1 = 100*`1`/sum(`1`),
         p2 = 100*`2`/sum(`2`)) %>%
  select(quantile_group_collapsed, `1`, p1, `2`, p2) %>%
  kable(caption = "Summary of subjects in highest quantile by diagnosis",
        col.names = c("Retest impaired domain", "N", "%", "N", "%"),
        digits = c(0, 0, 1, 0, 1)) %>%
  kable_styling(bootstrap_options = kable.styling.bootstrap.option,
                full_width = F, position = kable.styling.position.option) %>%
  add_header_above(c(" " = 1, "Normal" = 2, "MCI" = 2)) %>%
  column_spec(2, width = "6em") %>%
  column_spec(3, width = "5em") %>%
  column_spec(4, width = "5em") %>%
  column_spec(5, width = "5em") %>%
  row_spec(0, align = "c")

```

