
```{r}
rm(list = setdiff(ls(), lsf.str())[!(setdiff(ls(), lsf.str()) %in% "params")])
source(here::here("R", "002-folder_paths_and_options.R"))

# It's input is the following R objects:
# adni.survival.cn.mci <- readRDS(file=path(r_objects_folder, "025_adni_survival_cn_mci.rds"))
adni.survival.mci <- readRDS(file=path(r_objects_folder, "030_adni_survival_mci.rds"))
```

# Time to event analyses

This section examines the time to conversion for participants with MCI to AD.  It uses Kaplan Meier curves and Cox proportional hazards models.  The Kaplan Meier curves are stratified by the categorized change in language subdomain score. The Cox proportional hazards models use the second category ("no change") as the reference group.


```{r}

my_kaplanmeier <- function(x, df, mytitle, mylabels=NULL) {

  ggsurvplot(x, data = df,
           risk.table = FALSE,
           break.time.by = 1, 
           xlab = "Time from baseline (Years)",
           palette = c("#e41a1c", "#377eb8", "#4daf4a", "#984ea3", 
                       "#ff7f00", "#ffff33", "#a65628", "#f781bf"),
           ggtheme = hrbrthemes::theme_ipsum(),
           legend = "right",
           legend.labs = mylabels) +
  labs(title = mytitle)
}

my_cox_summary_table <- function(mod, mytitle, 
                                 highlight.color = "#FFFFCC", 
                                 highlight.pvalue = 0.05) {
  gtsummary::tbl_regression(mod, exp = TRUE) %>%
    gtsummary::as_gt() %>%
    tab_header(title = mytitle) %>%
    tab_style(
      style = list(
        cell_fill(color = highlight.color)
        ),
      locations = cells_body(
        rows = p.value < highlight.pvalue)
      )
}

```

```{r}
my_surv_object_mci <- with(adni.survival.mci, Surv(time_in_adni, event))
```

## Animal naming

### Kaplan Meier curve

```{r, fig.retina=2}
x_mci <- survfit(my_surv_object_mci ~ animalsc_raw_change_quantile, data = adni.survival.mci)
my_kaplanmeier(x_mci, adni.survival.mci,
               mylabels = c("1 (improve)", "2 (no change)", "3 (decline)"),
               mytitle = "Conversion from baseline MCI to AD by \n Change in animal score categorized") 
```

### Cox proportional hazards model

```{r}
fit.coxph.animal_raw.mci <- coxph(my_surv_object_mci ~ anim_raw_q1 + anim_raw_q3, 
                       data = adni.survival.mci)


my_cox_summary_table(fit.coxph.animal_raw.mci, mytitle = "Cox proportional hazards model - Change in animal fluency categories")
```

## F fluency

### Kaplan Meier curve

```{r, fig.retina=2}
x_mci <- survfit(my_surv_object_mci ~ ffluency_raw_change_quantile, data = adni.survival.mci)
my_kaplanmeier(x_mci, adni.survival.mci,
               mylabels = c("1 (improve)", "2 (no change)", "3 (decline)"),
               mytitle = "Conversion from baseline MCI to AD by \n Change in F fluency score categorized") 
```

### Cox proportional hazards model

```{r}
fit.coxph.f_raw.mci <- coxph(my_surv_object_mci ~ f_raw_q1 + f_raw_q3, 
                       data = adni.survival.mci)

my_cox_summary_table(fit.coxph.f_raw.mci, mytitle = "Cox proportional hazards model - Change in F fluency categories")
```

## Confrontation naming

### Kaplan Meier curve

```{r, fig.retina=2}
x_mci <- survfit(my_surv_object_mci ~ confront_change_quantile, data = adni.survival.mci)
my_kaplanmeier(x_mci, adni.survival.mci,
               mylabels = c("1 (improve)", "2 (no change)", "3 (decline)"),
               mytitle = "Conversion from baseline MCI to AD by \n Change in confrontation naming categorized") 
```

### Cox proportional hazards model

```{r}
fit.coxph.confront.mci <- coxph(my_surv_object_mci ~ confront_q1 + confront_q3, 
                       data = adni.survival.mci)

my_cox_summary_table(fit.coxph.confront.mci, mytitle = "Cox proportional hazards model - Change in confrontation naming categories")
```

## Boston Naming Test

### Kaplan Meier curve
```{r, fig.retina=2}
x_mci <- survfit(my_surv_object_mci ~ bnt_change_quantile, data = adni.survival.mci)
my_kaplanmeier(x_mci, adni.survival.mci,
               mylabels = c("1 (improve)", "2 (no change)", "3 (decline)"),
               mytitle = "Conversion from baseline MCI to AD by \n Change in Boston Naming Test categorized") 

```

### Cox proportional hazards model

```{r}
fit.coxph.bnt.mci <- coxph(my_surv_object_mci ~ bnt_q1 + bnt_q3, 
                       data = adni.survival.mci)

my_cox_summary_table(fit.coxph.bnt.mci, mytitle = "Cox proportional hazards model - Change in Boston Naming Test categories")

```


## Confrontation naming without BNT

### Kaplan Meier curve
```{r, fig.retina=2}
x_mci <- survfit(my_surv_object_mci ~ confront_wo_bnt_change_quantile, data = adni.survival.mci)
my_kaplanmeier(x_mci, adni.survival.mci,
               mylabels = c("1 (improve)", "2 (no change)", "3 (decline)"),
               mytitle = "Conversion from baseline MCI to AD by \n Change in confrontation naming without BNT categorized") 

```

### Cox proportional hazards model

```{r}
fit.coxph.confront.wo.bnt.mci <- coxph(my_surv_object_mci ~ confront_wo_bnt_q1 + confront_wo_bnt_q3, 
                       data = adni.survival.mci)

my_cox_summary_table(fit.coxph.confront.wo.bnt.mci, mytitle = "Cox proportional hazards model - Change in confrontation naming without BNT categories")

```

## Other language items

### Kaplan Meier curve
```{r, fig.retina=2}
x_mci <- survfit(my_surv_object_mci ~ others_change_quantile, data = adni.survival.mci)
my_kaplanmeier(x_mci, adni.survival.mci,
               mylabels = c("1 (improve)", "2 (no change)", "3 (decline)"),
               mytitle = "Conversion from baseline MCI to AD by \n Change in other language items categorized") 

```

### Cox proportional hazards model

```{r}
fit.coxph.others.mci <- coxph(my_surv_object_mci ~ others_q1 + others_q3, 
                       data = adni.survival.mci)

my_cox_summary_table(fit.coxph.others.mci, mytitle = "Cox proportional hazards model - Change in other language items categories")

```



